---
title: "Shiny Application and Reproducible Pitch"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
***
## Project Goal
This peer assessed assignment has two parts:

1. You will create a Shiny application and deploy it on Rstudio's servers.
2. You will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

***
## Steps to Perform
1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application.
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github

***
## How to use the application
Simple shiny app which shows four distribution plots for length and width of petals and sepals after one of the IRIS Species is selected in the sidebar. 

The dataset used for this project is IRIS which is available in R.

```{r}
head(iris)
```

****
## Application Information

The application is running on (https://abinashiprakash.shinyapps.io/Reproducible_Pitch/)

ui.R, and Server.R Code in my github repository (https://github.com/abinashi-prakash/Reproducible_Pitch)
